%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{PROJECTS}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Evaluation Model of Light Pollution by Multi-conditional AHP | MCM} % Project
    {Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Performed GIS-data analysis and mathematical modeling to assess light pollution levels based on population data and regional income.}
        \item {Utilized GeoPandas and Folium for data analysis and visualization, contributing to a comprehensive understanding of the impacts of light pollution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {1st and Future - Player Contact Detection Competition | Kaggle} % Project
    {Dec 2022 - Mar 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Advanced data preprocessing and integration for video analysis and player tracking, leading to a Bronze Medal achievement.}
        \item {Innovated predictive features through statistical modeling, significantly enhancing model accuracy in contact detection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Theory Analysis of SEO Strategies: From Methods to Models} % Project
    {Nov 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Researched and applied SEO strategies, developed a new ranking algorithm focusing on keyword frequency, traffic, and linkage.}
        \item {Implemented game theory principles to SEO, including simulation of an α-random walk and analysis of Nash Equilibrium.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AI-Based Flight Delay Insurance Recommendation System} % Project
    {Jun 2024 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developing a system to predict flight delays and recommend personalized travel insurance using deep learning, NLP, and sentiment analysis.}
        \item {Focused on enhancing customer satisfaction through accurate delay predictions and tailored insurance recommendations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Open Problems - Multimodal Single-Cell Integration | Kaggle} % Project
    {Feb 2022 - Apr 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Engaged in machine learning and data analysis to predict co-variances in DNA, RNA, and protein measurements in single cells, achieving a Silver Medal.}
        \item {Contributed to advancing understanding in multimodal single-cell data integration and analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Happywhale - Whale and Dolphin Identification | Kaggle} % Project
    {Aug 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Applied machine learning techniques for identifying whales and dolphins from photographic imagery, securing a Silver Medal.}
        \item {Enhanced data analysis methods to recognize unique characteristics, significantly improving identification accuracy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CPU Circuit Design | Class Project} % Project
    {Jul 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed and implemented simple RISC-V instructions through circuit design, achieving CPU pipelining.}
        \item {Focused on understanding and applying core concepts of computer architecture and digital logic design.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
